\documentclass{article}
\usepackage{parskip}
\usepackage[utf8]{inputenc}
\usepackage{titling}
\setlength{\droptitle}{-9em} 
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{cite}
\linespread{1.4}
\usepackage{hyperref}

\begin{document}
\title{CS 229 Project Proposal - Text Complexity, NLP}
\author{Harry Sha (harry2), Tyler Yep (tyep)}
\maketitle

\section{Introduction}
The goal of our project is to explore the idea of text complexity in the context of machine learning. More specifically, the questions we will answer are the following:
\begin{enumerate}
    \item What features of the text are most relevant to this classification?
    \item To what extent can machine learning methods be used to classify the complexity of a document?
    \item Can we build a model to generate or transform text into different levels of complexity?
\end{enumerate}

This project's outcomes have the potential of enhancing education immensely. Complexity-classified documents allow students to find papers or conceptual explanations at understandable difficulty level. Generating or transforming text into simpler levels of complexity encourages more widespread knowledge, approachable from different fields and backgrounds. Students gain the power to understand big picture ideas and ramp up the difficulty level as they see fit, ultimately resulting in a more personalized educational experience.

\section{Data: Feature Extraction and Selection}
We are working with the Weebit Dataset (TODO something about the dataset here)
\subsection{Data preprocessing}
To preprocess the data, we removed new line characters, set all words to be lower case and removed any trademark disclaimers. We also split the dataset into training, validation and test sets.

\subsection{Word count} TODO %Harry
\subsection{Tf-Idf} TODO %Harry
\subsection{Natural language features} TODO
\subsection{Basic analytics on natural language features} %Harry


\section{Model Selection}
TODO Have some figure/table here

\subsection{Baseline}%Harry
\subsection{Logistic Regression} %Harry
TODO have some figure comparing $C$ parameter to the validation accuracy.

\subsection{SVM}%Harry
\subsection{AdaBoost}\dots
\subsection{Other}

\section{Next Steps}
%HARRY

\begin{enumerate}
    \item \textbf{Hyperparameter Tuning and Cross Validation.}To further tune the hyperparameters of our models, we plan to employ random search with k-folds validation. In particular, random search has a greater change of exploring the whole parameter space due to the randomness (TODO cite https://www.analyticsindiamag.com/why-is-random-search-better-than-grid-search-for-machine-learning/). Further the use of k-folds validation allows us to incorporate the validation set in training. Furthermore, as the score in k-folds validation is computed as an average over the performance on each fold, we are less likely to overfit to any validation set. Hopefully, using these methods, we can further improve the performance our models.
    \item \textbf{LSTM (sequence model).} One key drawback in our representation of the documents is that most of the sequential information is lost in the encoding. However, it is very likely that the sequential relationships play a key role in determining the complexity of a text. The reason why sequential encodings were not used originally. 

    \item \textbf{Generative Algorithm}
\end{enumerate}


\section{Data and Resources}
\begin{enumerate}
    \item Weebit (Dataset) \begin{verbatim} http://www.aclweb.org/anthology/W13-2907\end{verbatim}
    \item Cambridge English Exam (Dataset) \begin{verbatim} https://www.cl.cam.ac.uk/~mx223/cedata.html\end{verbatim}
    \item Real-Time Analysis of Reading Difficulty (Research) \begin{verbatim} https://www.cs.rochester.edu/~tetreaul/Miltsakaki.pdf\end{verbatim}
    \item Automatic Text Difficulty Classifier for European Portuguese Teaching (Research) \begin{verbatim} http://www.inesc-id.pt/publications/11043/pdf\end{verbatim}
\end{enumerate}

\bibliographystyle{plain}
\bibliography{bibliography}

%\section{Plan}
%\subsection{Classification of Complexity}
%We will then experiment with many types of classification algorithms such as SVMs, linear models, k-nearest neighbours, decision trees, and deep learning models such as LSTMs. The different approaches can then be compared/evaluated and potentially used in ensemble, and then will be evaluated using cross-validation. 
%
%Complexity in past papers have been defined in different ways, from Lexile scores to age ranges, which we can experiment with. Ultimately, the complexity measurement we choose will stem from the datasets we analyze, however we do also have the option of reclassifying complexity data into broader categories.
%
%We also intend to explore non-traditional way of classifying complexity, perhaps inspired by the popular WIRED video series "5 Levels of Difficulty". Here, complexity is classified into child, teenager, adult, professional, and expert, which are very distinct categories. These distinct categories will cause the important distinctions to surface within our model, which we can then leverage in our final step, which is generating text at varying difficulties.
%
%\subsection{Generation of Text}
%Finally, we will create a model that generates or transforms text to different difficulties, or recreating the same text in a different complexity category. In particular, we are interested in simplifying complex texts - finding ways to express the same explanation of a concept, but understandable to a more general audience. Some initial ideas for implementations are to use LSTMs or GANs, which have seen success in generating sequences and images respectively. 
%
%One major application of this research goal is in academia - specifically, in the increasing readability difficulty of research papers. One reach goal of this project would be to find ways to safely and effectively simplify jargon into more colloquial forms, without sacrificing the overall meaning. To evaluate this model, we will find or create a rubric to distinguish the different complexity classes. Then, we will manually compare the generated output to our established rubric to measure the success of our model.
%
%By making research more accessible to the public, we would invite more collaborators into complex fields, ultimately accelerating the growth rate of human knowledge.
\end{document}
